### 2024-01-29 Project/Metsim_P2_Kelompok04.Rmd
Update

---
title: "Tugas Praktikum 1"
author: "Angga Fathan Rofiqy"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmdformats::downcute:
    self_contained: true
    thumbnails: false
    lightbox: true
    gallery: true
    highlight: tango
    code_folding: show
    toc_depth: 3
    number_sections: false
    toc_float:
      collapsed: true
      smooth_scroll: true
    fig_caption: true
pkgdown:
  as_is: true
---