### 2024-01-29 Project/Metsim_P2_Kelompok04.Rmd
Update

---
title: "Tugas Praktikum 1"
author: "Angga Fathan Rofiqy"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmdformats::downcute:
    self_contained: true
    thumbnails: false
    lightbox: true
    gallery: true
    highlight: tango
    code_folding: show
    toc_depth: 3
    number_sections: false
    toc_float:
      collapsed: true
      smooth_scroll: true
    fig_caption: true
pkgdown:
  as_is: true
---

```{r message=FALSE, warning=FALSE, include=FALSE}
#                      -=( Install & Load Package Function )=-
install_load <- function (package1, ...)  {

   # convert arguments to vector
   packages <- c(package1, ...)

   # start loop to determine if each package is installed
   for(package in packages){

       # if package is installed locally, load
       if(package %in% rownames(installed.packages()))
          do.call('library', list(package))

       # if package is not installed locally, download, then load
       else {
          install.packages(package)
          do.call("library", list(package))
       }
   } 
}
```

# No 3

![](images/clipboard-3975775370.png){width="584"}

```{r}

```

# No 4

![](images/clipboard-1149010623.png)

```{r}

```